Logarithmic Space Verifiers on NP-complete

### 2019-11-18 doc/manuscript.tex
Fixing grammar doc

Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.

>>>>

Sauerhoff has investigated the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$) \cite{MS03}.
